Automated Formal Synthesis\\ of Safe Digital Controllers for Continuous Plants

### 2019-01-23 automatica/paper.tex
is this better for the fixed point arithmetic on intervals?

The fixed-point arithmetic of the digital controller is performed on the upper and lower bound of each interval independently and the upper and lower bound of the result taken as the interval result\note{clarify what is meant by 'limit' and by 'each' (each amongst what?)}.  
Since the precision of the floating point domain is greater than the precision of the controller, this is guaranteed to bound the real behaviour of the controller.

>>>>

The fixed-point arithmetic of the digital controller is performed on the upper and lower bound of the intervals independently and the upper and lower bound of the result taken as the interval result\note{Would an example make this clearer?, e.g., consider the conversion from plant precision to controller precision performed by the ADC on a single state value. The state value is represented as an interval $\{x.high, x.low\}$, and the result of the conversion is an interval where the upper bound is the conversion of $x.high$ and the lower bound is the conversion of $x.low$?}. 
Since the precision of the floating point domain is greater than the precision of the controller, this is guaranteed to bound the real behaviour of the controller.
